Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2018-02-01 WSSSPE4_report/WSSSPE4_paper.tex
2 changes as suggested in email by Wolfgang
small changes related to proofreading for JORS

@@

%
\thanks{{}$^{(1)}$ National Center for Supercomputing Applications (NCSA) \&
Department of Computer Science  \&
Department of Electrical and Computer Engineering  \&
School of Information Sciences (iSchool),
University of Illinois, Urbana--Champaign, IL, USA; d.katz@ieee.org; ORCID: 0000-0001-5934-7525}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering,
Oregon State University, Corvallis, OR, USA; kyle.niemeyer@oregonstate.edu; ORCID: 0000-0003-4425-7097}
%
\thanks{{}$^{(3)}$ Center for Research Computing \& Department of Computer Science and Engineering,
University of Notre Dame, IN, USA; sandra.gesing@nd.edu; ORCID: 0000-0002-6051-0673}
%
\thanks{{}$^{(4)}$ University of California, Davis, CA, USA; ljhwang@ucdavis.edu; ORCID: 0000-0002-1021-3101}
%
\thanks{{}$^{(5)}$ Department of Mathematics, Colorado State
  University, Fort Collins, CO, USA; bangerth@colostate.edu; ORCID: 0000-0003-2311-9402}
%
\thanks{{}$^{(6)}$ The Software Sustainability Institute, Southampton, UK; s.hettrick@software.ac.uk; ORCID: 0000-0002-6809-5195}
%
\thanks{{}$^{(7)}$ RENCI, University of North Carolina at Chapel Hill, Chapel Hill, NC, USA; rayi@renci.org; ORCID: 0000-0002-3444-7615}
%
\thanks{{}$^{(8)}$ University of Virginia, Charlottesville, VA, USA; jeansalac@virginia.edu; ORCID: 0000-0001-5971-9333}
%
\thanks{{}$^{(9)}$ University of Edinburgh, UK; N.ChueHong@epcc.ed.ac.uk;
ORCID: 0000-0002-8876-7606}
%
\thanks{{}$^{(10)}$ Illinois Informatics Institute (I3) and National Center for Supercomputing Applications (NCSA), University of Illinois at Urbana-Champaign, IL, USA;
nunezco2@illinois.edu;
ORCID: 0000-0003-4342-6223}
%
\thanks{{}$^{(11)}$ Astrophysics Source Code Library, Astronomy Department, University of Maryland, College Park, MD, USA; aallen@ascl.net; ORCID: 0000-0003-3477-2845}
%
\thanks{{}$^{(12)}$ University of California, Berkeley, Berkeley Institute for Data Science (BIDS), Berkeley, CA, USA; stuart@stuartgeiger.com; ORCID: 0000-0001-7215-0532}
%
\thanks{{}$^{(13)}$ Perimeter Institute for Theoretical Physics \&
Department of Physics, University of Guelph,
Guelph, ON, Canada;
jmiller@perimeterinstitute.ca; ORCID: 0000-0001-6432-7860}
%
\thanks{{}$^{(14)}$ University of Illinois at Urbana-Champaign, USA; echen35@illinois.edu; ORCID: 0000-0003-2578-0296}
%
\thanks{{}$^{(15)}$ Mathematics and Computer Science Division,
Argonne National Laboratory,
Lemont, IL, USA \&
University of Chicago,
Chicago, IL, USA;
Adubey@anl.gov;
ORCID: 0000-0003-3299-7426}
%
\thanks{{}$^{(16)}$ Vrije Universiteit Amsterdam, The Netherlands; p.lago@vu.nl; ORCID: 0000-0002-2234-0845}

@@

This article summarizes motivations, organization, and activities of the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4). The WSSSPE series promotes sustainable research software by positively impacting principles and best practices, careers, learning, and credit. This article includes the code of conduct; the mission and vision statements that were drafted at the workshop and finalized shortly after it; the keynote and idea papers, position papers, experience papers, demos, and lightning talks presented during the workshop; and a panel discussion on best practices. The main part of the article discusses the set of working groups that formed during the meeting, along with contact information for readers who may want to join a group. Finally, it discusses a survey of the workshop attendees.

@@

WSSSPE4 introduced a Code of Conduct (CoC)\footnote{\label{footnote:CoC}\url{http://wssspe.researchcomputing.org.uk/wssspe4/code-of-conduct/}}, which was conceived for the workshop and as guidance for the community of scientists that WSSSPE
supports, including their personal and online interactions (e.g., on
Twitter, in email lists, in Slack). This CoC is based on the
FORCE11 conference CoC~\cite{FORCE11:CoC}, which is in turn based on the Code4Lib
CoC~\cite{Code4Lib:CoC}.
The main guidelines are:
\begin{quote}
    WSSSPE events are community events intended for networking and collaboration
    as well as learning. We value the participation of every member of the
    community and want all attendees to have an enjoyable and fulfilling
    experience. Accordingly, all attendees are expected to show respect and
    courtesy to other attendees throughout the event and in interactions online
    associated with the event.

>>>>

\usepackage{cite}

@@

%
\thanks{{}$^{(1)}$ National Center for Supercomputing Applications (NCSA) \&
Department of Computer Science  \&
Department of Electrical and Computer Engineering  \&
School of Information Sciences (iSchool),
University of Illinois, Urbana--Champaign, IL, USA; d.katz@ieee.org; ORCID: 0000-0001-5934-7525}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering,
Oregon State University, Corvallis, OR, USA; kyle.niemeyer@oregonstate.edu; ORCID: 0000-0003-4425-7097}
%
\thanks{{}$^{(3)}$ Center for Research Computing \& Department of Computer Science and Engineering,
University of Notre Dame, IN, USA; sandra.gesing@nd.edu; ORCID: 0000-0002-6051-0673}
%
\thanks{{}$^{(4)}$ University of California, Davis, CA, USA; ljhwang@ucdavis.edu; ORCID: 0000-0002-1021-3101}
%
\thanks{{}$^{(5)}$ Department of Mathematics, Colorado State
  University, Fort Collins, CO, USA; bangerth@colostate.edu; ORCID: 0000-0003-2311-9402}
%
\thanks{{}$^{(6)}$ The Software Sustainability Institute, Southampton, UK; s.hettrick@software.ac.uk; ORCID: 0000-0002-6809-5195}
%
\thanks{{}$^{(7)}$ RENCI, University of North Carolina at Chapel Hill, Chapel Hill, NC, USA; rayi@renci.org; ORCID: 0000-0002-3444-7615}
%
\thanks{{}$^{(8)}$ University of Chicago, Chicago, IL, USA; salac@uchicago.edu; ORCID: 0000-0001-5971-9333}
%
\thanks{{}$^{(9)}$ University of Edinburgh, UK; N.ChueHong@epcc.ed.ac.uk;
ORCID: 0000-0002-8876-7606}
%
\thanks{{}$^{(10)}$ Illinois Informatics Institute (I3) and National Center for Supercomputing Applications (NCSA), University of Illinois at Urbana-Champaign, IL, USA;
nunezco2@illinois.edu;
ORCID: 0000-0003-4342-6223}
%
\thanks{{}$^{(11)}$ Astrophysics Source Code Library, Astronomy Department, University of Maryland, College Park, MD, USA; aallen@ascl.net; ORCID: 0000-0003-3477-2845}
%
\thanks{{}$^{(12)}$ University of California, Berkeley, Berkeley Institute for Data Science (BIDS), Berkeley, CA, USA; stuart@stuartgeiger.com; ORCID: 0000-0001-7215-0532}
%
\thanks{{}$^{(13)}$ Perimeter Institute for Theoretical Physics \&
Department of Physics, University of Guelph,
Guelph, ON, Canada;
jmiller@perimeterinstitute.ca; ORCID: 0000-0001-6432-7860}
%
\thanks{{}$^{(14)}$ University of Illinois at Urbana-Champaign, USA; echen35@illinois.edu; ORCID: 0000-0003-2578-0296}
%
\thanks{{}$^{(15)}$ Mathematics and Computer Science Division,
Argonne National Laboratory,
Lemont, IL, USA \&
University of Chicago,
Chicago, IL, USA;
Adubey@anl.gov;
ORCID: 0000-0003-3299-7426}
%
\thanks{{}$^{(16)}$ Vrije Universiteit Amsterdam, The Netherlands; p.lago@vu.nl; ORCID: 0000-0002-2234-0845}

@@

This article summarizes motivations, organization, and activities of the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4). The WSSSPE series promotes sustainable research software by positively impacting principles and best practices, careers, learning, and credit. This article discusses the code of conduct; the mission and vision statements that were drafted at the workshop and finalized shortly after it; the keynote and idea papers, position papers, experience papers, demos, and lightning talks presented during the workshop; and a panel discussion on best practices. The main part of the article discusses the set of working groups that formed during the meeting, along with contact information for readers who may want to join a group. Finally, it discusses a survey of the workshop attendees.

@@

WSSSPE4 introduced a Code of Conduct (CoC)\footnote{\label{footnote:CoC}\url{http://wssspe.researchcomputing.org.uk/wssspe4/code-of-conduct/}}, which was conceived for the workshop and as guidance for the community of scientists that WSSSPE
supports, including their personal and online interactions (e.g., on
Twitter, in email lists, in Slack). This CoC is based on the
FORCE11 conference CoC~\cite{FORCE11:CoC}, which is in turn based on the Code4Lib
CoC~\cite{Code4Lib:CoC}.
In introducing the CoC, we asked participants to agree to the following main guidelines:
\begin{quote}
    WSSSPE events are community events intended for networking and collaboration
    as well as learning. We value the participation of every member of the
    community and want all attendees to have an enjoyable and fulfilling
    experience. Accordingly, all attendees are expected to show respect and
    courtesy to other attendees throughout the event and in interactions online
    associated with the event.
